
\chapter*{Abstract}
\par This report summarizes the work carried out within the Finaxys and its client Amundi Asset Management, as part of the internship for obtaining the State Engineer Diploma Specialty: Computer, Electronic, Systems and Network Engineering at the National School of Applied Sciences in Oujda.  \\
\par Finaxys, a consulting firm specializing in IT finance, has many clients: BNP Paribas, Societe generale, Credit Agricole\dots and Amundi AM which is considered as a strategic client and partner. The European and world leader in asset management is divided into several sub-entities. I have been assigned to the OST/ITS/INV/MDM department, MDM for Master Data Management. \\
\par MDM brings together all the teams managing applications that use sensitive data from Amundi AM called Master Data. I have been assigned to two major projects, Media Plus Core and Alto Investment Research. \\
\par MediaplusCore is an application/server for diffusion and broadcast of various market data to its users. For example, portfolio data, index data, issuers and equity data... The server is developed under JAVA 7 and a migration to JAVA 8 was performed around September 2020. I had the chance to interact with several parts of the project, including the creation of new REST APIs and the addition and modification of EJB for data broadcast. \\
\par Alto Investment Research is a front-office application developed with Maestro, a framework based on the Angular 8 framework, whose goal is to provide and transform an old interface to new screens created by UI/UX designers in order to offer users a complete and easy to use interface. This application is used by Amundi AM business engineers (Traders, Sales\dots). \\
\par Management tools such as Jira and Gitlab are used daily by the team members developing the two projects.
\\~\\~\\~\\~\\~\\~\\~\\
\par Keywords: JAVA, Angular, Maestro, Jira, Gitlab, Asset Management, Amundi, Finaxys